Miniproject - Elliptic Curves

### 2022-03-30 Elliptic Curves/submission.tex
Fixed an example for Elliptic Curves

    Conversely, assume that $E$ is isomorphic to an Elliptic Curve of the above form, so wlog
    \begin{equation*}
        E: y^2 + x y + v y = x^3 + v x^2
    \end{equation*}
    We show that $(0, 0) \in E(\Q)$ has order $4$.
    The tangent has slope $0$, so is given by the line $y = 0$.
    The third point of intersection with $E$ is now $(-v, 0)$.
    Note that the line through $(-v, 0)$ and $\O$ has the equation $x = -v$ and meets $E$ at $(-v, 0)$ with multiplicity 2.
    It follows that $(-v, 0)$ is a 2-torsion point, and so $E(\Q)$ has the point $(0, 0)$ of order 4.
\end{proof}
It looks like we could continue in a similar way for e.g. 6-or 7-torsion points, but the algebra becomes more and more convoluted. 
\begin{example}[3(ii) - first example]
    Consider the Elliptic Curve
    \begin{equation*}
        E: y^2 + x y + y = x^3
    \end{equation*}
    defined over $\Q$.
    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve (If $3x^2 - y = 2y + 1 + x \equiv 0$ then $y \equiv 0$ and $x \equiv -1$, but $(-1, 0) \notin \tilde{E}(\F_3)$).
    Trying all values in $\F_3^2$, we find
    \begin{equation*}
        \tilde{E}(\F_3) = \{ (0, 0), (0, 2), \O \} 
    \end{equation*}
    Clearly $E(\Q)$ has the 3-torsion point $(0, 0)$, and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_3)$ we see that
    \begin{equation*}
        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (0, -1), \O \}
    \end{equation*}
\end{example}
\begin{example}[3(ii) - second example]
    Consider the Elliptic Curve
    \begin{equation*}
        E: y^2 + x y + 2 y = x^3 + 2 x^2
    \end{equation*}
    defined over $\Q$.
    Note that the reduction $\tilde{E}$ modulo $5$ is still an Elliptic Curve (If $3x^2 + y = 2y + 1 + x = 0$ then $y^2 - y - 1 = 0$, so $y = -1$ and $x = 1$. However $(1, -1) \notin \tilde{E}(\F_3)$).
    Trying all values in $\F_3^2$, we find
    \begin{equation*}
        \tilde{E}(\F_3) = \{ (0, 0), (0, 2), \O \} 
    \end{equation*}
    Clearly $E(\Q)$ has the 3-torsion point $(0, 0)$, and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_3)$ we see that
    \begin{equation*}
        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (0, -1), \O \}
    \end{equation*}
\end{example}

>>>>

    Conversely, assume that $E$ is isomorphic to an Elliptic Curve of the above form, so wlog
    \begin{equation*}
        E: y^2 + x y + v y = x^3 + v x^2
    \end{equation*}
    We show that $(0, 0) \in E(\Q)$ has order $4$.
    The tangent has slope $0$, so is given by the line $y = 0$.
    The third point of intersection with $E$ is now $(-v, 0)$.
    Note that the line through $(-v, 0)$ and $\O$ has the equation $x = -v$ and meets $E$ at $(-v, 0)$ with multiplicity 2.
    It follows that $(-v, 0)$ is a 2-torsion point, and so $E(\Q)$ has the point $(0, 0)$ of order 4.
\end{proof}
It looks like we could continue in a similar way for e.g. 6-or 7-torsion points, but the algebra becomes more and more convoluted. 
\begin{example}[3(ii) - first example]
    Consider the Elliptic Curve
    \begin{equation*}
        E: y^2 + x y + y = x^3
    \end{equation*}
    defined over $\Q$.
    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve 
    (if $3x^2 - y \equiv 2y + 1 + x \equiv 0$ then $y \equiv 0$ and $x \equiv -1$, but $(-1, 0) \notin \tilde{E}(\F_3)$).
    Trying all values in $\F_3^2$, we find
    \begin{equation*}
        \tilde{E}(\F_3) = \{ (0, 0), (0, 2), \O \} 
    \end{equation*}
    Clearly $E(\Q)$ has the 3-torsion point $(0, 0)$, and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_3)$ we see that
    \begin{equation*}
        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (0, -1), \O \}
    \end{equation*}
\end{example}
\begin{example}[3(ii) - second example]
    Consider the Elliptic Curve
    \begin{equation*}
        E: y^2 + x y + 2 y = x^3 + 2 x^2
    \end{equation*}
    defined over $\Q$.
    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve
    (if $3x^2 + 4x - y \equiv 2y + x + 2 \equiv 0$ then $x - y \equiv x - y - 1 \equiv 0$, a contradiction).
    Trying all values in $\F_3^2$, we find
    \begin{equation*}
        \tilde{E}(\F_3) = \{ (0, 0), (0, 1), (1, 0), \O \} 
    \end{equation*}
    Now note that $E(\Q)$ has the 4-torsion point $(0, 0)$ and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_5)$ we already see that
    \begin{equation*}
        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (-2, 0), (0, -2), \O \}
    \end{equation*}
\end{example}
